\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-22 main.Rmd
text of new example

Figure \ref{fig:dow} shows the energy use across days of week in the form of letter value plots [@hofmann2017letter]. As a variant of boxplots, letter value plots represent each pair of adjacent letter values using one box, instead of whiskers. Figure \ref{fig:dow} demonstrates three letter values and outliers marked as asterisks, with a line representing the median (thus M) and the innermost boxes corresponding to the fourth (F) and the eighth quantiles (E). Household 3, with a family size of one couple and two kids, uses more energy over the week days given the medians, compared to the others consisting of one or two people. Whereas, household 2 displays a great deal of variability in daily energy consumption with noticeable variations on Thursdays, and much higher usage over the weekends. The other two households (1 and 4) tend to consume more energy on average with increased variations during the weekends relative to the week days, as a reflection of work and leisure patterns.

@@

Figure \ref{fig:hod} provides a more detailed depiction of each household's life style, by plotting energy consumption against time of day between week days and weekends. Household 1 is an early bird, starting their day before 6 and going back home around 18 on week days. They switch air conditioning or heating on when they get home from work and keep it operated till mid-night, while learned from the tiny cluster of points below 1 kWh. On the other hand, the strips above 1 kWh tells that household 2 perhaps have air conditioning or heating on all time during the days, consuming the energy almost as double as household 1. Apart from the morning and night peak use, a third peak occurs around 3pm for household 3 only, when the kids are home from school. They also share a consistent energy pattern between week days and weekends. As for household 4, their home routine starts after 6pm on week days. Figure \ref{fig:dow} and \ref{fig:hod}, part of traditional graphical toolkits, are useful for summarizing overall deviations across days and households.

@@

Figure \ref{fig:h12} and \ref{fig:h34} apply the new calendar displays individually for each household, unfolding their day-to-day life. Glancing through Figure \ref{fig:h12}, their week day energy use distinguishes from their weekends. We can exactly tell when their air conditioner and heater are turned on. Heating keeps functioning in consecutive hours at household 2, which is evident in the mid July; while household 1 uses them cautiously. This finding helps explain the strips and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous figures. Household 1 is on vacation over three weeks of June, and household 2 was also away for holidays during Christmas and the second week of June. Figure \ref{fig:h34} shows household 3 takes two one-month-long family trips in September till early October and in June/July, and household 4 is away over two or three weeks in early October, December and late June. The use of air conditioning and heating leaves no trace in these two households.

@@

The calendar-based visualization provides data plots in the familiar format of an everyday tool. Patterns on special events for the region, like Anzac Day in Australia, or Thanksgiving Day in the USA, more easily pop out to the viewer as public holidays, than they would on a more commonly used week day and month faceted layout.

The methodology creates the western calendar layout, because most countries have adopted this format. The main difference between countries is the use of different languages for labelling, which is supported by the software. Layouts beyond the western calendar could be achieved by the same modulars arithmetic approach.

>>>>

Figure \ref{fig:dow} shows the energy use across days of week in the form of letter value plots [@hofmann2017letter]. Letter value plots are a variant of boxplots for large data, with other quantiles represented by boxes. Letters indicate the fraction of the data divisions, for example, F indicates fourths or quartiles, and the two outer ends of the box are the 25th and 75th percentile, the same traditional ends of the box as a boxplot. The letter E indicates eighths, with box ends being 12.5th and 87.5th percentiles of the data. These additional boxes replace the whiskers in a traditional boxplot. The letter value plots for the households, show a line indicating the median (M) and the innermost boxes corresponding to the fourth (F) and the eighth (E) quantile divisions. Inspecting the medians across households tells us that household 3, a family size of one couple and two kids, uses more energy over the week days, than other households. The relatively larger boxes for household 2 indicates greater variability in daily energy consumption with noticeable variations on Thursdays, and much higher usage over the weekends. The other two households (1 and 4) tend to consume more energy with more  variation on the weekends relative to the week days, reflecting of work and leisure patterns.

@@

Figure \ref{fig:hod} shows energy consumption against time of day, separately by week day and weekend. Household 1 is an early bird, starting their day before 6 and going back home around 18 on week days. They switch air conditioning or heating on when they get home from work and keep it operating till mid-night, learned from the small horizontal cluster of points around 0.8 kWh. On the other hand, the stripes above 1 kWh for  household 2 indicates that perhaps air conditioning or heating runs continuously for some periods, consuming the twice the energy as household 1. A third peak occurs around 3pm for household 3 only, likely when the kids are home from school. They also have a consistent energy pattern between week days and weekends. As for household 4, their home routine starts after 6pm on week days.

@@

Figures \ref{fig:dow} and \ref{fig:hod}, part of a traditional graphical toolkit, are useful for summarizing overall deviations across days and households. Figure \ref{fig:h12} and \ref{fig:h34} display the data in calendar layout individually for each household, unfolding their day-to-day life. Glancing through Figure \ref{fig:h12}, their week day energy use distinguishes from their weekends. We can exactly tell when their air conditioner and heater are turned on. Heating keeps functioning in consecutive hours at household 2, which is evident in the mid July; while household 1 uses them cautiously. This finding helps explain the strips and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous figures. Household 1 is on vacation over three weeks of June, and household 2 was also away for holidays during Christmas and the second week of June. Figure \ref{fig:h34} shows household 3 takes two one-month-long family trips in September till early October and in June/July, and household 4 is away over two or three weeks in early October, December and late June. The use of air conditioning and heating leaves no trace in these two households.

@@

The calendar-based visualization provides data plots in the familiar format of an everyday tool. Patterns on special events for the region, like Anzac Day in Australia, or Thanksgiving Day in the USA, are more visible to the viewer as public holidays.

The methodology creates the western calendar layout, because most countries have adopted this format. The main difference between countries is the use of different languages for labelling, which is supported by the software. Layouts beyond the western calendar could be achieved by the same modular arithmetic approach.

### 2018-10-22 main.tex
text of new example

Figure \ref{fig:dow} shows the energy use across days of week in the
form of letter value plots \citep{hofmann2017letter}. As a variant of
boxplots, letter value plots represent each pair of adjacent letter
values using one box, instead of whiskers. Figure \ref{fig:dow}
demonstrates three letter values and outliers marked as asterisks, with
a line representing the median (thus M) and the innermost boxes
corresponding to the fourth (F) and the eighth quantiles (E). Household
3, with a family size of one couple and two kids, uses more energy over
the week days given the medians, compared to the others consisting of
one or two people. Whereas, household 2 displays a great deal of
variability in daily energy consumption with noticeable variations on
Thursdays, and much higher usage over the weekends. The other two
households (1 and 4) tend to consume more energy on average with
increased variations during the weekends relative to the week days, as a
reflection of work and leisure patterns.

>>>>

Figure \ref{fig:dow} shows the energy use across days of week in the
form of letter value plots \citep{hofmann2017letter}. Letter value plots
are a variant of boxplots for large data, with other quantiles
represented by boxes. Letters indicate the fraction of the data
divisions, for example, F indicates fourths or quartiles, and the two
outer ends of the box are the 25th and 75th percentile, the same
traditional ends of the box as a boxplot. The letter E indicates
eighths, with box ends being 12.5th and 87.5th percentiles of the data.
These additional boxes replace the whiskers in a traditional boxplot.
The letter value plots for the households, show a line indicating the
median (M) and the innermost boxes corresponding to the fourth (F) and
the eighth (E) quantile divisions. Inspecting the medians across
households tells us that household 3, a family size of one couple and
two kids, uses more energy over the week days, than other households.
The relatively larger boxes for household 2 indicates greater
variability in daily energy consumption with noticeable variations on
Thursdays, and much higher usage over the weekends. The other two
households (1 and 4) tend to consume more energy with more variation on
the weekends relative to the week days, reflecting of work and leisure
patterns.
